### 2020-01-31 thesis_template/2_RelatedWork/relatedWork.tex
resolved experiment

@@

>>>>

\section{Access time to onwned, borrowed, and sliced field of object}
\label{sec:history}
In this experiment, differences of access time among to owned, borrowed, and sliced are observed. 
The figure is representation of a Customer object. Among the experiment, we focus on zip_code, address, country fields. 
These three fields take differet type of String value. The zip_code field takes owned String variable. 
The address field takes borrowed String variable. The country field takes slice String variable. 
The assumption here is that there may be difference of operation time among variable types: ownner, reference, slice.

The result shows that access times to onwer and reference are almost the same, but the one to slice is relatively faster 
compared to the other two.

\begin{figure}[htb]
    \begin{lstlisting}
        struct Customer<'a> {
            total_order: i32,
            weight_order: f32,
            zip_code: String,
            address: &'a String,
            country: &'a str
        }
    \end{lstlisting}
    \caption{Representation of Customer object in Rust.}
    \label{fig:Sampling}
\end{figure}

@@

Design experiment for Trait object and Generic function. 
We can have Trait object which is pointer to object which imprements its Trait and use the method of Trait object.
This object has additional information other than just reference to tye original object. 
This is because Rust needs the type information to dynamically calll the right method of Trait object depending on the type of 
original object.
On the other hand, we can have Generic function whose parameter types are Generic types corresponding to Trait. 
When Rust compiles the code, it emits independent function corresponding to every types that implements the Trains specified in parameter.

Vector of Trait(need to put element into Box) vs Vector of concrete type.
